New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2023-05-09 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
Demo_Tabelle

classoption       : "man"
output            : bookdown::word_document2 
# papaja::apa6_pdf

@@

# changing gender to count female gender (male = 2 --> 0)
df_demo$gender = ifelse(df_demo$gender == 2, "1","0")

# changing character Gender into numeric
df_demo$gender <- as.numeric(df_demo$gender)

@@

# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
df_demo$school_type[df_demo$school_type == 2] <- "1"

@@

# changing character Percent_schooltype into numeric
df_demo$percent_schooltype <- as.numeric(df_demo$percent_schooltype)

@@

# create a basic table (tibble) using tidyverse functions
df_demo_table <- df_demo %>%
  ungroup() %>%
  summarise(N=n(),
            "Gender female in percent" = round(sum(gender/sum_participants) * 100,
                                               digits = 2),
            "M Age in years" = round(mean(age),
                                     digits = 2),
            "SD Age in years" = round(sd(age),
                                      digits = 2),
            "Min Age in years" = min(age),
            "Max Age in years" = max(age),
            "M Teaching Experience in years" = round(mean(teaching_experience),
                                            digits = 2),
            "SD Teaching Experience in years" = round(sd(teaching_experience),
                                            digits = 2),
            "Min Teaching Experience in years" = min(teaching_experience),
            "Max Teaching Experience in years" = max(teaching_experience)
            )

# # format and insert table in manuscript
# df_demo_table %>%
# papaja::apa_table(
#   caption = "Demographic Information",
#   # note = "Write Note here",
#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
#   )

>>>>

classoption       : "man"
output            : papaja::apa6_pdf

@@

# changing gender to count female gender (female = 2 --> 1, male --> 0)
df_demo$gender = ifelse(test = df_demo$gender == 2,
                        yes = 1,
                        no = 0)

# changing character Gender into numeric
# df_demo$gender <- as.numeric(df_demo$gender)

# recoding gender - Freddy

@@

# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
df_demo$school_type[df_demo$school_type == 2] <- 1

@@

# changing character Percent_schooltype into numeric
# df_demo$percent_schooltype <- as.numeric(df_demo$percent_schooltype)

@@

# create a basic table (tibble) using tidyverse functions
df_demo_table <- df_demo %>%
  ungroup() %>%
  summarise('N' = round(mean(sum_participants),
                             digits = 0),
            "Gender female in percent" = round(sum(gender/sum_participants) * 100,
                                               digits = 2),
            "M Age in years" = round(mean(age),
                                     digits = 2),
            "SD Age in years" = round(sd(age),
                                      digits = 2),
            "Min Age in years" = min(age),
            "Max Age in years" = max(age),
            "M Teaching Experience in years" = round(mean(teaching_experience),
                                            digits = 2),
            "SD Teaching Experience in years" = round(sd(teaching_experience),
                                            digits = 2),
            "Min Teaching Experience in years" = min(teaching_experience),
            "Max Teaching Experience in years" = max(teaching_experience)
            )

df_demo_table_long <- pivot_longer(data = df_demo_table,
                              cols = everything(),
                              names_to = 'Variable',
                              values_to = 'values')

# # format and insert table in manuscript
 df_demo_table_long %>%
 papaja::apa_table(
   caption = "Demographic Information",
#   # note = "Write Note here",
   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
   )

### 2023-05-09 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
Demo_Tabelle

The sample consisted in total of \emph{N} = 72 pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 70 subjects.

The subjects (42 women; 60 \%) had a mean age of 29.70 years (\emph{SD} = 10.70; range: 19-59) and an average teaching experience of 4.84 years (\emph{SD} = 9.31; range: 0-37).

17.14\% of the subjects were (studying to become) teachers for primary school, 70\% were (studying to become) teachers for secondary school and 11.43\% were (studying to become) teachers for special education needs.

@@

We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.2.9; Revelle, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

@@

Teachers' average heart rate during the entire course of the study was approximately 96.84 bpm with a standard deviation of 14.44 and a range from 56 to 139 bpm.

@@

>>>>

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:demographicstable}Demographic Information}

\tiny{

\begin{tabular}{ll}
\toprule
Variable & \multicolumn{1}{c}{values}\\
\midrule
N & 76.00\\
Gender female in percent & 63.16\\
M Age in years & 30.26\\
SD Age in years & 10.52\\
Min Age in years & 19.00\\
Max Age in years & 59.00\\
M Teaching Experience in years & 5.17\\
SD Teaching Experience in years & 9.12\\
Min Teaching Experience in years & 0.00\\
Max Teaching Experience in years & 37.00\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

The sample consisted in total of \emph{N} = 76 pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 76 subjects.

The subjects (48 women; 63.16 \%) had a mean age of 30.30 years (\emph{SD} = 10.50; range: 19-59) and an average teaching experience of 5.17 years (\emph{SD} = 9.12; range: 0-37).

15.79\% of the subjects were (studying to become) teachers for primary school, 71.05\% were (studying to become) teachers for secondary school and 10.53\% were (studying to become) teachers for special education needs.

@@

We used R (Version 4.2.2; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.48; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.2; Wickham, 2021), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{jtools} (Version 2.2.1; Long, 2022), \emph{lm.beta} (Version 1.7.2; Behrendt, 2022), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.58.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.1.9001; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Revelle, 2022), \emph{purrr} (Version 0.3.5; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.1; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.1; Kassambara, 2021), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tibble} (Version 3.1.8; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.2; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.38; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

@@

Teachers' average heart rate during the entire course of the study was approximately 90.40 bpm with a standard deviation of 15.82 and a range from 51 to 164 bpm.

@@

\begin{verbatim}
## Warning: Unknown levels in `f`: pre, main, subsequent, interview, after
\end{verbatim}
